Integrated multi-omics analysis reveals Lactobacillus anti-inflammatory process in vaginal tissue

### 2021-03-03 reports/rmarkdown/manuscript/manuscript_template.Rmd
updates KEGG and correlation matricies

##############################
# METADATA CROSS-ASSOCIATION #
##############################
par(mar=c(12,1,1,12))
image( t(clean_Ftest [nrow(clean_Ftest):1,]),axes=F,
       col=colorRampPalette(c("grey95","grey70","orange3","firebrick"))(90) )
text(  par("usr")[2]+.02 ,seq(1,0,length.out = nrow(clean_Ftest)) ,
       labels = rownames(clean_Ftest), srt = 0, adj = c(0,.5), xpd = TRUE, cex=1)
text( seq(0,1,length.out = nrow(clean_Ftest)) , par("usr")[3]-.02 ,
      labels = rownames(clean_Ftest), srt = 90, adj = c(1,.5), xpd = TRUE, cex=1)

@@

pvals <- sapply(res2, function(x){x[,"pvalue"]})
rs <- sapply(res2, function(x){x[,"r.squared"]})

@@

plot(0,0, las=1,xlim=c(.5,ncol(rs)+.5),ylim=c(.5,nrow(rs)+.5),
       axes=F,ylab="",xlab="",main=gsub("^ASV_|_norm.*","",k),xaxs="i",yaxs="i", frame=T)
for(i in 1:ncol(rs)){
  lines(c(i,i),c(nrow(rs)+.5,0),col="grey95",lwd=.5,xpd=F)
}
for(i in 1:nrow(rs) ){
  lines(c(0,ncol(rs)+0.5),c(i,i),col="grey95",lwd=.5,xpd=F)
}
points(sort(rep(1:ncol(rs),nrow(rs))),
      rep(nrow(rs):1,ncol(rs)),
        col=colorRampPalette(c("navy","grey95","firebrick"))(91)[cut( c(rs) , breaks = seq(-1,1,length.out = 92) )],pch=16 ,
      cex= sizes*2 + 0.2)
srt=90
text(1:ncol(rs), par("usr")[3] - (par("usr")[4])/200, labels = colnames(rs), srt = srt,
     adj = c(ifelse(srt==0,.5,ifelse(srt==90,1,1)),ifelse(srt==0,1,ifelse(srt==90,.5,1))),
     xpd = TRUE, cex=1)
add_letter(figlabels[1]); figlabels <- figlabels[-1]
}

empty_plot(xlim=c(.5,ncol(rs)+.5),ylim=c(.5,nrow(rs)+.5),xaxs="i",yaxs="i")
text(par("usr")[1] , 1:nrow(rs) , labels = rownames(rs), srt = 0, adj = c(0,0.5), xpd = TRUE, cex=1)

@@

```{r, echo = FALSE, eval = TRUE, fig.asp=.5}
metadata_parameters <- colnames(metadata)[-c(1:2)]

@@

sizes <- as.matrix(-log10(clean_Ftest))
# sizes[sizes < 2] <- 0
sizes[sizes > 7] <- 7
sizes <- sizes / max(sizes)
sizes <- sizes * lower.tri(sizes)

mypar(1,1,mar=c(10,10,2,6))
plot(0,0, las=1,xlim=c(.5,ncol(sizes)+.5),ylim=c(.5,nrow(sizes)+.5),
       axes=F,ylab="",xlab="",main="",xaxs="i",yaxs="i", frame=T)
for(i in 1:ncol(sizes)){
  lines(c(i,i),c(nrow(sizes)+.5,0),col="grey95",lwd=.5,xpd=F)
}
for(i in 1:nrow(sizes) ){
  lines(c(0,ncol(sizes)+0.5),c(i,i),col="grey95",lwd=.5,xpd=F)
}
points(sort(rep(1:ncol(sizes),nrow(sizes))),
      rep(nrow(sizes):1,ncol(sizes)),
        col=colorRampPalette(c("grey95","orange3","firebrick","black"))(91)[cut( c(sizes) , breaks = seq(0,1,length.out = 92) )],pch=16 ,
      cex= sizes*1 + 0.2)
srt=90
text(1:ncol(sizes), par("usr")[3] - (par("usr")[4])/200, labels = colnames(sizes), srt = srt,
     adj = c(ifelse(srt==0,.5,ifelse(srt==90,1,1)),ifelse(srt==0,1,ifelse(srt==90,.5,1))),
     xpd = TRUE, cex=1)
text(par("usr")[1] , 1:nrow(sizes) , labels = rownames(sizes), srt = 0, adj = c(1,0.5), xpd = TRUE, cex=1)

@@

```{r, echo = FALSE, eval = TRUE,fig.asp=.3}
figlabels <- letters
for(j in names(module_means_per_dataset)){
  mypar(2,8,mar=c(0.5,0.5,4,0.5))

  plot(UMAP_picrust,bg=pal[group_annotation],main="patient groups",
     pch=21,xlab="UMAP1",ylab="UMAP2",frame=F,axes=F)
  add_letter(figlabels[1]); figlabels <- figlabels[-1]

@@

    xx <- module_means_per_dataset[[j]][i,]
    xx <- xx / max(xx)
    o <- order(xx)
    plot(UMAP_picrust[o,],
         col=colorRampPalette( c("grey95","navy")) (99)[ 1 + (xx[o]*98) ],
         main=rownames(module_means_per_dataset[[j]])[i],
         pch=16,xlab="UMAP1",ylab="UMAP2",frame=F,axes=F,font.main=1,cex.main=1)
  }
}
```

@@

```{r, echo = FALSE, eval = TRUE,fig.asp=.3}
figlabels <- letters
for(j in names(module_means_per_dataset)){
  mypar(2,8,mar=c(0.5,0.5,4,0.5))

  plot(UMAP_TRX,bg=pal[group_annotation[sample_use]],main="patient groups",
     pch=21,xlab="UMAP1",ylab="UMAP2",frame=F,axes=F)
  add_letter(figlabels[1]); figlabels <- figlabels[-1]

@@

    xx <- module_means_per_dataset[[j]][i,][sample_use]
    xx <- xx / max(xx)
    o <- order(xx)
    plot(UMAP_TRX[o,],
         col=colorRampPalette( c("grey95","navy")) (99)[ 1 + (xx[o]*98) ],
         main=rownames(module_means_per_dataset[[j]])[i],
         pch=16,xlab="UMAP1",ylab="UMAP2",frame=F,axes=F,font.main=1,cex.main=1)
  }
}
```

@@

```{r, echo = FALSE, eval = TRUE,fig.asp=1.2}
figlabels <- letters
mypar(3,3,mar=c(4,10,2,2))
for( j in c("ASV_tissue_V3_normalized_batch_corrected",
        "ASV_CVL_V3_normalized_batch_corrected",
        "ASV_CVL_V2_normalized_NOT_batch_corrected")){
  temp_group <- as.character(group_annotation)
  temp_group[ is.na(temp_group) ] <- "NA"
  temp_group[ temp_group == "" ] <- "NA"
  temp_group <- factor(temp_group)

@@

```{r, echo = FALSE, eval = TRUE,fig.asp=1.2}
mypar(mar=c(10,6,1,1))

>>>>

##############################
# METADATA CROSS-ASSOCIATION #
##############################
par(mar=c(12,1,1,12))
set.seed(1)
noise <- matrix(rnorm(prod(dim(clean_Ftest)),mean = 0,sd = 1e-10),nrow(clean_Ftest),ncol(clean_Ftest))
o <- hclust(as.dist( (1-cor(clean_Ftest+noise)/2) ),method = "ward.D2")$order

sizes <- as.matrix(clean_Ftest[o,o])
sizes[sizes > 7] <- 7
sizes <- sizes / max(sizes)
image( t(sizes [nrow(sizes):1,]),axes=F,
       col=colorRampPalette(c("grey95","grey70","orange3","firebrick"))(90) )
text(  par("usr")[2]+.02 ,seq(1,0,length.out = nrow(sizes)) ,
       labels = rownames(sizes), srt = 0, adj = c(0,.5), xpd = TRUE, cex=1)
text( seq(0,1,length.out = nrow(sizes)) , par("usr")[3]-.02 ,
      labels = rownames(sizes), srt = 90, adj = c(1,.5), xpd = TRUE, cex=1)

@@

pvals <- sapply(res2, function(x){x[,"pvalue"]})
rs <- sapply(res2, function(x){x[,"r.squared"]})
rs[is.nan(rs)] <- 0
pvals[is.nan(pvals)] <- 1

@@

plot(0,0, las=1,xlim=c(.5,ncol(rs)+.5),ylim=c(.5,nrow(rs)+.5),
       axes=F,ylab="",xlab="",main=gsub("^ASV_|_norm.*","",k),xaxs="i",yaxs="i", frame=T)
for(i in 1:ncol(rs)){
  lines(c(i,i),c(nrow(rs)+.5,0),col="grey95",lwd=.5,xpd=F)
}
for(i in 1:nrow(rs) ){
  lines(c(0,ncol(rs)+0.5),c(i,i),col="grey95",lwd=.5,xpd=F)
}
points(sort(rep(1:ncol(rs),nrow(rs))),
      rep(nrow(rs):1,ncol(rs)),
        col=colorRampPalette(c("navy","grey95","firebrick"))(91)[cut( c(rs) , breaks = seq(-1,1,length.out = 92) )],pch=16 ,
      cex= sizes*2 + 0.2)
srt=90
text(1:ncol(rs), par("usr")[3] - (par("usr")[4])/200, labels = colnames(rs), srt = srt,
     adj = c(ifelse(srt==0,.5,ifelse(srt==90,1,1)),ifelse(srt==0,1,ifelse(srt==90,.5,1))),
     xpd = TRUE, cex=.8)
add_letter(figlabels[1]); figlabels <- figlabels[-1]
}

empty_plot(xlim=c(.5,ncol(rs)+.5),ylim=c(.5,nrow(rs)+.5),xaxs="i",yaxs="i")
text(par("usr")[1] , 1:nrow(rs) , labels = rownames(rs), srt = 0, adj = c(0,0.5), xpd = TRUE, cex=.8)

@@

```{r, echo = FALSE, eval = TRUE, fig.asp=.9}
metadata_parameters <- colnames(metadata)[-c(1:2)]

@@

sizes <- as.matrix(clean_Ftest[o,o])
# sizes[sizes < 2] <- 0
sizes[sizes > 7] <- 7
sizes <- sizes / max(sizes)
sizes <- sizes * lower.tri(sizes)

mypar(1,1,mar=c(10,10,2,6))
plot(0,0, las=1,xlim=c(.5,ncol(sizes)+.5),ylim=c(.5,nrow(sizes)+.5),
       axes=F,ylab="",xlab="",main="",xaxs="i",yaxs="i", frame=T)
for(i in 1:ncol(sizes)){
  lines(c(i,i),c(nrow(sizes)+.5,0),col="grey95",lwd=.5,xpd=F)
}
for(i in 1:nrow(sizes) ){
  lines(c(0,ncol(sizes)+0.5),c(i,i),col="grey95",lwd=.5,xpd=F)
}
points(sort(rep(1:ncol(sizes),nrow(sizes))),
      rep(nrow(sizes):1,ncol(sizes)),
        col=colorRampPalette(c("grey95","orange3","firebrick","black"))(91)[cut( c(sizes) , breaks = seq(0,1,length.out = 92) )],pch=16 ,
      cex= sizes*1 + 0.2)
srt=90
text(1:ncol(sizes), par("usr")[3] - (par("usr")[4])/200, labels = colnames(sizes), srt = srt,
     adj = c(ifelse(srt==0,.5,ifelse(srt==90,1,1)),ifelse(srt==0,1,ifelse(srt==90,.5,1))),
     xpd = TRUE, cex=1)
text(par("usr")[1] , nrow(sizes):1 , labels = rownames(sizes), srt = 0, adj = c(1,0.5), xpd = TRUE, cex=1)

@@

```{r, echo = FALSE, eval = TRUE,fig.asp=1.3}
layout( matrix(1:(16*8), 16,8,byrow = F) )
par(mar=c(.5,.5,1,.5))

figlabels <- letters
for(j in names(module_means_per_dataset)){

  plot(UMAP_picrust,bg=pal[group_annotation],main=gsub("ASV_|_norm.*","",j),
     pch=21,xlab="UMAP1",ylab="UMAP2",frame=F,axes=F)
  add_letter(figlabels[1]); figlabels <- figlabels[-1]

@@

    xx <- module_means_per_dataset[[j]][i,]
    xx <- xx / max(xx)
    o <- order(xx)
    plot(UMAP_picrust[o,],
         col=colorRampPalette( c("grey95","navy")) (99)[ 1 + (xx[o]*98) ],
         main="",
         pch=16,xlab="UMAP1",ylab="UMAP2",frame=F,axes=F,font.main=1,cex.main=1)
  }
}
empty_plot()

text( par("usr")[1], mean(par("usr")[3:4]),
        adj=c(0,0.5),xpd=T,
        labels = "patient groups" )
for(i in 1:nrow(module_means_per_dataset[[j]])){
  empty_plot()
  text( par("usr")[1], mean(par("usr")[3:4]),
        adj=c(0,0.5),xpd=T,
        labels = sub( "_","\n",rownames(module_means_per_dataset[[j]])[i]) )
}

@@

```{r, echo = FALSE, eval = TRUE,fig.asp=1.3}
layout( matrix(1:(16*8), 16,8,byrow = F) )
par(mar=c(.5,.5,1,.5))

figlabels <- letters
for(j in names(module_means_per_dataset)){

  plot(UMAP_TRX,bg=pal[group_annotation[sample_use]],main=gsub("ASV_|_norm.*","",j),
     pch=21,xlab="UMAP1",ylab="UMAP2",frame=F,axes=F)
  add_letter(figlabels[1]); figlabels <- figlabels[-1]

@@

    xx <- module_means_per_dataset[[j]][i,][sample_use]
    xx <- xx / max(xx)
    o <- order(xx)
    plot(UMAP_TRX[o,],
         col=colorRampPalette( c("grey95","navy")) (99)[ 1 + (xx[o]*98) ],
         main="",xpd=T,
         pch=16,xlab="UMAP1",ylab="UMAP2",frame=F,axes=F,font.main=1,cex.main=1)
  }
}

empty_plot()
text( par("usr")[1], mean(par("usr")[3:4]),
        adj=c(0,0.5),
        labels = "patient groups" )
for(i in 1:nrow(module_means_per_dataset[[j]])){
  empty_plot()
  text( par("usr")[1], mean(par("usr")[3:4]),
        adj=c(0,0.5),xpd=T,
        labels = sub( "_","\n",rownames(module_means_per_dataset[[j]])[i]) )
}

@@

```{r, echo = FALSE, eval = TRUE,fig.asp=.8}
figlabels <- letters
mypar(3,3,mar=c(4,12,2,4))
for( j in c("ASV_tissue_V3_normalized_batch_corrected",
        "ASV_CVL_V3_normalized_batch_corrected",
        "ASV_CVL_V2_normalized_NOT_batch_corrected")){
  temp_group <- as.character(group_annotation)
  temp_group[ is.na(temp_group) ] <- "NA"
  temp_group[ temp_group == "" ] <- "NA"
  temp_group <- factor(temp_group)

@@

```{r, echo = FALSE, eval = TRUE,fig.asp=.5}
mypar(mar=c(10,6,1,1))

### 2021-03-03 reports/rmarkdown/manuscript/manuscript_template.tex
updates KEGG and correlation matricies

\title{Integrated multi-omics analysis reveals Lactobacillus anti-inflammatory process in vaginal tissue}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A demonstration of Rmarkdown using Herman Bumpus' data}
\author{Author One\textsuperscript{1},
Author Two\textsuperscript{2},
Author Three\textsuperscript{1,2}}
\date{February 23, 2021}

@@

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-13-1}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-13-2}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-13-3}

@@

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-14-1}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-14-2}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-14-3}

>>>>

\title{Integrated multi-omics analysis reveals Lactobacillus anti-inflammatory process in vaginal tissue}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A demonstration of Rmarkdown using Herman Bumpus' data}
\author{Author One\textsuperscript{1},
Author Two\textsuperscript{2},
Author Three\textsuperscript{1,2}}
\date{March 03, 2021}

@@

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-13-1}

@@

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-14-1}
